Comparing Different Planned Missingness Designs in Longitudinal Studies

### 2018-05-16 Documentation/manuscript.Rnw
manuscript.

\begin{document}

@@

Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are so named because of the way in which they are implemented. Instead of giving participants one large survey, researchers will create multiple “forms”, each containing only a subset of the full survey’s questions. A common setup is the three-form design \citep{graham1996maximizing}. In the three-form design the full survey is split into four blocks, X, A, B, and C. Each form of the survey includes the X block as well as two of the other three blocks. This leaves us with the configurations seen in Table \ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded. We note that every block is paired together in at least one of the forms. By designing our forms in this manner we are able to estimate the relationship between any given items regardless of which blocks they are in. That is, if we want to estimate the relationship between an item in block A and another in C, there is a form that allows us to do that. \par

@@

If we have prior knowledge concerning the relationship between unobserved values, indicated by $R$, and the observed values, then Multiple Imputation can yield efficient estimates even under MNAR \citep{harel2007multiple}. However, because this is not typically the case MI is most often implemented when data is MCAR or MAR \citep{little2014statistical}. \par 
As a consequence of allowing researchers to decide which values in a dataset are observed and unobserved, PM designs grant control over the missing data mechanism. Because of this, MI is an appealing option for researchers utilizing a PM design. If implemented properly, data should conform to either the MCAR or MAR assumption. For instance, if medical researchers decide not to collect blood pressure on a completely random subset of patients there is no reason to believe the missing blood pressures differ significantly from the observed ones. This fact allows for the use of MI and other modern missing data techniques such as the Full Information Maximum Likelihood approach \citep{dempster1977maximum} \par

\subsubsection{The Multiple Imputation Procedure}
\label{sec:1.3.2}
Multiple Imputation is used to obtain statistically valid inferences in spite of missing data. MI works by replacing unobserved values with a set of plausible values in a way which allows us to account for uncertainty in the imputation process. Repeatedly using some imputation technique every missing value in the incomplete dataset is replaced with a fixed number of imputed values. This process allows for the creation of multiple complete datasets, on which users can run complete-data procedures. If, for instance, we imputed $M$ possible values for every missing value we would obtain $M$ different completed datasets. Once these datasets have been created, we can run the analysis of interest on each of them and, using rules defined by \citet{little2014statistical} and \citet{rubin2004multiple}, combine our results to obtain a single inference. \par

@@

These equations form the basis of Rubin's combining rules and should provide parameter estimates which are unbiased while accounting for the inherent uncertainty in the imputation process \citep{raghunathan2015missing}. For a more in depth explanation of these methods we refer readers to \citet{little2014statistical}. \par

When using Multiple Imputation researchers must decide on the number of imputations, $M$, to use. Generally speaking, the lower the level of missingness is the fewer imputations are needed. If less than 20\% of the requisite data is missing, for instance, ten or even five imputations will suffice \citep{raghunathan2015missing}. However, at its roots MI is a simulation technique and thus, the greater $M$ is the more stable our estimates become \citep{harel2007inferences}. \citet{graham2007many} recommend that if computational power is not a limiting factor, then setting $M=100$ is good practice. \par

\section{Data and Simulations}
\label{sec:2}
\subsection{Data}
\label{sec:2.1}
The dataset we based our simulations on came from a study by \citet{pellowski2016alcohol} and more in depth information on it can be found there. However, to give a brief overview, the data was collected in an attempt to determine the day-level relationship between alcohol use, interactive toxicity beliefs, and adherence to antiretroviral therapy (ART) amongst patients with HIV. Previous studies noted that alcohol use combined with the perception that mixing alcohol and ARTs can cause adverse effects, correlated with non-adherence to ARTs \citep{kalichman2009prevalence, kalichman2012alcohol}. However, \citet{pellowski2016alcohol} pointed out that past research had collected data over extended periods of time preventing the identification a day-level interaction. Unlike others, this study was able to determine whether alcohol use and missed medication doses occurred on the same day. \par

The study employed an observational cohort design, following sixty participants over forty-five days and sending them a daily questionnaire. Questions in the survey concerned livelihood insecurities from the previous day as well as alcohol use. The analysis used eight particular questions, two binary questions on housing insecurity, four binary questions on food insecurity, and two questions concerning alcohol use  (one binary variable and one count variable). The exact questions can be found in Table \ref{tab:table1}. \par

@@

\subsection{Simulations}
\label{sec:2.2}
The first step in the process of creating our simulated datasets was to use the data from \citet{pellowski2016alcohol} and obtain parameter estimates to quantify the relationships between variables. We then treated these estimated relationships as the “true” relationships and drew two-hundred samples using these parameters. While we would have liked to simulate a larger number of samples we were limited by computational ability. Our purpose in simulating these datasets was to see how well they would be able to capture the true relationship between medication adherence on a certain day, whether or not a participant drank that day, and their beliefs about alcohol-medication interactivity (included as a Z-transformed test score). Specifically, our model of interest is the random intercept model with time effect found below: \\

@@

Additionally, for each different Missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 25\%, 50\%, and 75\% missing data. Previous work by \citet{rhemtulla2014planned} has found that for low levels of missingness (25\%) the Three-Form design outperforms the Wave Missingness design in its ability to capture latent growth curve model parameters. However, because only low-levels of missingness are tested we do not know if this relationship holds at moderate or high levels. We hope that by including these different levels of missingness we will be able to see how these designs perform at all levels of the missingness spectrum. \par
Once missingness was created we used Multiple Imputation techniques to estimate the relationship between Medication Adherence and the other variables in our model. Because we have control over the missing data mechanism, we know the data is MCAR. This fact allows for the principled use of MI techniques. Using the R package $\{$mice$\}$ \citep{mice2011imputation} our binary variables (Q1-Q7) were imputed using a logistic model based approach while the count variable (Q8) was imputed using predictive mean matching. \par

After imputations the logistic random-intercept model was estimated for each of the imputed datasets and combined using Rubin's Rules \citep{rubin2004multiple}. From here, the results from each PM design were evaluated based on bias, percent bias, mean squared error (MSE), coverage, confidence interval (CI) length, and the fraction of missing information (FMI). The FMI is a measure of how much of the MI sampling variance comes from differences between imputations. Besides comparing the results between each of the PM designs we also included the results of these same analyses taken from before missingness was imposed. \par

When determining if the PM designs are performing sufficiently well it is important to consider how well the simulated samples performed before we added a missingness structure. For example, imagine we have two full data samples with respective biases on the $\beta_1$ estimate of 0.13 and 0.15. Further, after imposing different PM design structures on these samples we obtained the average biases of 0.14 and 0.15 respectively. It would be unfair to claim that the first
PM design performed better than the second because, by chance, it was based off of a more representative sample. We kept this fact in mind when determining our evaluation criteria. \par

For bias, percent bias, and MSE we claimed that an increase of more than 40\% in these measurements after imposing missingness indicates that the PM design is inappropriate. For instance, if the complete data shows a percent bias of 10\%, anything higher than 14\% ($0.1*1.4$) would be unacceptable. An increase of this size has the ability to negatively effect efficiency of our estimation. Based on the work of \citet{collins2001comparison} we also regard coverages of less than 90\% as unacceptable. If a 95\% CI has a true coverage of 90\% than the Type I error rate is double what it should be. Because MI accounts for uncertainty in the imputation process coverages should have been similar despite the added missingness. In terms of confidence interval lengths, if one PM design provides similar rates of coverage to another while maintaining shorter intervals than this is considered the better of the two methods. For equal coverage rates, shorter intervals imply more power. The FMI, which quantifies the uncertainty in our imputation process, is simply reported for each PM design. While less uncertainty in the imputations can be beneficial, less variation does not necessarily imply accuracy. Thus, FMI should be taken in the context of the other measurements. \par

We repeated this process under three modified simulation scenarios mentioned in the following sections. We note that while typically these PM designs would be compared against the results obtained using a complete case analysis \citep{rhemtulla2016asymptotic} we decided against this approach because it would fundamentally alter the form of our data. To be more concrete, complete case analysis on the Split Form design would remove all observations (all observations have some missing values). In the Wave Missingness setup, complete case analysis would shorten the length of the longitudinal study. If a participant was missing values on 11 of the 45 days, then complete case analysis would have made the data resemble a longitudinal study held over 34 days. Hence, this comparison is invalid. \par

\subsubsection{Increased Sample Size}
In order to evaluate the impact of sample size on estimation we took the format of the original data, which included sixty participants, and expanded it to include one-hundred and twenty. The rest of the simulation process was carried out as before. We noted earlier that cost savings created from the PM designs could allow us to enroll more participants. Thus, even if one design performed more optimally than the others, if all designs also perform acceptably well at high samples, then researchers can design missingness in whichever method is most convenient. We further note, that because Wave Missingness allows for greater savings an increase in sample size is more reasonable for that type of Missingness. \par
\subsubsection{Low Inter-Survey Correlation}
For our second simulation scenario we looked to determine the effect of decreased inter-survey correlation on which PM design would perform best. To clarify, consider the fact that answers given on a particular day may be correlated with one another- the two questions on housing insecurity, for example, are likely to be "yes" on the same days. While this fact was accounted for in the original simulations, it was not in this set of simulations. If the probability of answering “yes” on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations then in this scenario it is a function of only the baseline variables. This implies that each of the questions are conditionally independent of each other given the baseline variables. If researchers have a questionnaire where they do not expect any of the answers to be obviously related the results here may help to choose which missingness design would be most optimal. \par
\subsubsection{High Time Effect}
In this final scenario we hoped to determine which PM design would lead to the best estimates when time has a disproportionately large effect on our outcome variable. To do this we changed the value of the parameters $\gamma_0, \beta_1, \beta_2,$ and $\beta_3$ to -4.6, 0.28, 0.64, and 0.2 respectively. We note that instead of increasing the value of $\beta_3$, the slope for time effect, we decreased all the other parameters. We did this because $\beta_3$ was already fairly large and increasing its value further would cause the probability of missing a dose to rapidly approach 1. By decreasing the other variables effects we were able to ensure that time has a disproportionate effect without incurring this problem. The results of this section may prove useful to researchers who believe that the overall passage of time plays a larger role in their outcome than a measurement taken at one specific point. \par

\section{Results}
\label{sec:3}
\subsection{Primary Simulation}
\label{sec:3.1}
The first set of simulations we ran had the parameters in our random-intercept logistic model set as $\gamma_0 = -2.3$, $\beta_1 = 0.56$, $\beta_2 = 1.28$, and $\beta_3 = 0.2$. The effects of the variables here are comparable to those found in the original dataset. This fact implies that we can interpret the results here to show what may have occurred if the original study had implemented a PM design. Before we imposed a missingness structure on our two-hundred simulated samples we obtained the full data results shown in Table \ref{tab:table2}. We note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.

<<>>=
load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_high.RData")
high <- d

load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_med.RData")
med <- d

load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_low.RData")
low <- d

@@

load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_high_hightime1.RData")
high <- d

load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_med_hightime1.RData")
med <- d

load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_low_hightime1.RData")
low <- d

@@

Of note in the complete-data primary analysis is that the coverage of our 95\% CIs is larger than expected for our parameter estimates and the percent bias for the $\beta_1$ estimate is somewhat large. This increased bias is likely due to the difficulties inherent in estimating logistic regression models with rare event data \citep{king2001logistic}. Nevertheless, we should keep this in mind when analyzing our results from the PM designs provided in Table \ref{tab:table3}. In Table \ref{tab:table3} as in Tables \ref{tab:table4}, \ref{tab:table5}, and \ref{tab:table6} bold values indicate "Unacceptable" results. That is, a Bias, Percent Bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.

@@

For the Split Form and Altered Split Form designs seen in Table \ref{tab:table3}, we note that the greatest loss in efficiency was on the $\beta_1$ estimate. While the CI coverage remained high at all levels of missingness for the two designs the bias, percent bias, and MSE reached unacceptable levels at the high missingness level. We also point out that the Altered Split Form design did not perform significantly better than the regular Split Form design. While some individual measurements outperformed those from the Split Form design, bias on $\beta_1$ for example, it underperformed in others, such as percent bias on $\beta_3$. In reference to the FMI on the $\beta_1$ estimate, we can see that at low and medium missingness both Split Form designs performed well. That is to say, there was less variance in the results from our imputed datasets than we expected given the amount of missing data.\par

Towards the bottom of Table \ref{tab:table3} we see that the Wave Missingness design provided unacceptable results on bias, percent bias, and MSE for the $\beta_1$ estimate at medium and high levels of missingness. Moreover, at high levels of missingness even coverage became unacceptable as coverage probabilities of the 95\% CIs dropped to 88.5\%.  Additionally, we see that CI length for the $\beta_1$ estimate was roughly equal across all designs, despite the fact that the Wave Missingness design provided more biased estimates. \par

\subsection{Increased Sample Size}
\label{sec:3.2}
The next simulation scenario we tested was under an increased sample size. All parameter values were held the same as in the original set of simulations but instead of simulating data for 60 participants here we used 120 participants. Table \ref{tab:table2}, again, contains the results of our analysis before applying any PM design. \par

We compare the results from the full-data simulations to those obtained from the PM designs, shown in Table \ref{tab:table4}. The first thing we notice is that the bias on all parameters is lower than it was in the smaller sample size simulations. Next, the Split Form design performed similarly well under this simulation scenario as in the first. At low levels of missingness it gave acceptable results for bias, percent bias, and MSE for the $\beta_1$ and for medium levels only the MSE was unacceptable. However, the CI length here is relatively far from the complete-data measurement in Table \ref{tab:table2}. The CI length from the complete-data simulations was 0.460 while at high levels of missingness the CI length reaches 1.088. We also point out that the percent bias on the $\beta_1$ estimate is not seriously different from that obtained in the small sample scenario. For example, at medium levels of missingness the percent bias on $\beta_1$ here is 23.86\% while for the smaller sample it was 23.75\%.
Similarly to the Split Form design, the Altered Split Form Design also provided unacceptable results for the MSE of the $\beta_1$ estimate at medium missingness and unacceptable bias, percent bias, and MSE at high levels.  \par
For the Wave Missingness design we continue to see the issues pointed out in the small sample simulations. That is, for the $\beta_1$ estimate we have unacceptable measurements at medium and high levels of missingness and a steep drop off in coverage probability for our 95\% CIs. In fact, at medium and high levels of missingness we find coverages of 85.5\% and 82.0\%. We also continue to see that the $\gamma_0$ parameter is being estimated poorly at high levels of missing data under the Wave Missingness design. \par

\subsection{Low Inter-Survey Correlation}
\label{sec:3.3}
For the next set of simulations we returned to the smaller sample size but decreased the level of inter-survey correlation. As mentioned in section 3.2.2 we made sure that there was no direct predictive relationship between questions in our survey. The results obtained from our full data simulations are provided in Table \ref{tab:table2} while the results from our PM designs are given in Table \ref{tab:table5}. \par

For the Split Form design it is important to notice that the efficiency of the $\beta_1$ estimate decreases much more rapidly than in our first set of simulations where survey questions were predictive of one another. For instance, the bias of $\beta_1$ at low levels of missingness, here, was found to be 0.150 and 0.276 at high levels. This left us with an increase in average bias of 0.126. If we check the same increase in the original simulations we see that the bias only increased by 0.071. This loss in efficiency is seen in the other measurements on the $\beta_1$ estimate as well. Moreover, we note that the Split Form design performs unacceptably in terms of bias, percent bias, and MSE at medium levels of missingness. This was not the case in the other missingness scenarios. \par

In the Altered Split Form design at medium levels of missingness the MSE is outside of the acceptable range and at high levels bias, are percent bias are unacceptable as well. We further note that the coverage of the $\beta_1$ CIs was quite a bit higher than in the full-data simulations. That is, while the coverage probability obtained in the full-data simulations was 94.5\%, under this Altered Split Form design we obtained coverages of 95.5\%, 97.0\%, and 96.0\% at low, medium, and high levels of missingness respectively. \par

Concerning the Wave Missingness design we, again, see the issues of unacceptable bias, percent bias and MSE. However, at low levels of missingness the coverage of our $\beta_1$ estimate was fairly good (96.5\% compared to 94.5\% in the full data). This positive coverage did not hold throughout the other levels of missingness as coverage dropped to 89.5\% in the high missingness scenario. As in other scenarios, the CI lengths produced under the Wave Missingness design are similar to those produced in the Split Form designs despite an increase in bias. However, this increase in bias is less dramatic than in other scenarios. For example, at high levels of missingness in the original simulations the average bias on the $\beta_1$ estimate was 0.065 higher for the Wave Missingness design (at 0.290) than in the Split Form design (0.225). In this simulation scenario that same difference was only 0.027. Moreover, while the estimation of $\gamma_0$ was unacceptable at high levels of missingness in the other simulation scenarios, here it was in the acceptable range.\par

\subsection{High Time Effect}
\label{sec:3.4}
In the final scenario we tested to see how the PM designs would capture a model where time had a disproportionately large effect. In this scenario parameter values were changed to $\gamma_0 = -4.6$, $\beta_1 = 0.28$, $\beta_2 = 0.64$, and $\beta_3 = 0.2$. The results from our full-data analyses are provided in Table \ref{tab:table2} while the corresponding PM design results are in Table \ref{tab:table6}. \par

@@

The Altered Split Form design performed slightly better than the normal Split Form design under this simulation scenario. We do note, though, that while the normal Split Form design provided unacceptable bias and percent bias for the $\beta_1$ estimate at medium levels of missingness, this was not true in the Altered Split Form design. Additionally, we point out that at medium and high levels of missingness we saw an improvement from the Split Form design in the CI lengths for the $\beta_1$ estimate. In the Split Form design the CI lengths were recorded as 0.981 and 1.433 at medium and high missingness. Under the Altered Split Form design these measurements were 0.903 and 1.381. \par

>>>>

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are very aptly named. Instead of giving participants one large survey, researchers create multiple forms, each containing a subset of the full survey's questions. A common form setup is the three-form design \citep{graham1996maximizing} in which the full survey is split into four blocks: X, A, B, and C. Each form of the survey includes the X block as well as two of the remaining blocks. This leaves the configurations seen in Table \ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded. Note that every block appears in at least one form. By designing the forms in this manner we are able to estimate the relationship between any chosen items regardless of their blocks. That is, if we want to estimate the relationship between an item in block A and another in C, there is a form that allows this. \par

@@

If we have prior knowledge concerning the relationship between unobserved values, indicated by $R$, and the observed values, then Multiple Imputation can yield efficient estimates even under MNAR \citep{harel2007multiple}. However, because this is not typically the case, MI is most often implemented when data is MCAR or MAR \citep{little2014statistical}. \par

As a consequence of allowing researchers to decide which values in a dataset are observed and unobserved, PM designs grant control over the missing data mechanism. Because of this, MI is an appealing option for researchers utilizing a PM design. If implemented properly, data should conform to either the MCAR or MAR assumption. For instance, if medical researchers decide not to collect blood pressure on a completely random subset of patients there is no reason to believe the missing blood pressures differ significantly from the observed ones. This fact allows for the use of MI and other modern missing data techniques such as the Full Information Maximum Likelihood approach \citep{dempster1977maximum} \par

\subsubsection{The Multiple Imputation Procedure}
\label{sec:1.3.2}
Multiple Imputation is used to obtain statistically valid inferences in spite of missing data. MI works by replacing unobserved values with a set of plausible values in a way which allows us to account for uncertainty in the imputation process. Repeatedly using an imputation technique, every missing value in the incomplete dataset is replaced with a fixed number of imputed values. This process allows for the creation of multiple complete datasets, on which users can run complete-data procedures. If, for instance, we imputed $M$ possible values for every missing value we would obtain $M$ different completed datasets. Once created, the analysis of interest can be performed on each of them and, using rules defined by \citet{little2014statistical} and \citet{rubin2004multiple}, combine the results to obtain a single inference. \par

@@

These equations form the basis of Rubin's combining rules and provide unbiased parameter estimates accounting for the inherent uncertainty in the imputation process \citep{raghunathan2015missing}. For a more in depth explanation of these methods we refer readers to \citet{little2014statistical}. \par

When using Multiple Imputation, researchers must decide on the number of imputations, $M$, to use. Generally, as the level of missingness decreases the number of imputations needed does as well. If less than 20\% of the requisite data is missing, for instance, five or tien imputations will suffice \citep{raghunathan2015missing}. However, at its roots, MI is a simulation technique and thus, the greater $M$ is the more stable our estimates become \citep{harel2007inferences}. \citet{graham2007many} recommend that if computational power is not a limiting factor, then setting $M=100$ is good practice. \par

\section{Data and Simulations}
\label{sec:2}
\subsection{Data}
\label{sec:2.1}
The dataset the simulations are based on originated in a study by \citet{pellowski2016alcohol}. The data was collected in an attempt to determine the day-level relationship between alcohol use, its interactive toxicity beliefs, and adherence to antiretroviral therapy (ART) amongst patients with HIV. Previous studies note that alcohol use combined with the perception that mixing alcohol and ARTs can cause adverse effects, correlated with non-adherence to ARTs \citep{kalichman2009prevalence, kalichman2012alcohol}. However, \citet{pellowski2016alcohol} pointed out that past research collected data over extended periods of time, preventing the identification a day-level interaction. Unlike others, this study was able to determine whether alcohol use and missed medication doses occurred on the same day. \par

The study employed an observational cohort design, following sixty participants over forty-five consequtive days via a daily questionnaire. Questions in the survey concerned livelihood insecurities from the previous day as well as alcohol use. The analysis included eight particular questions: two binary questions on housing insecurity, four binary questions on food insecurity, and two questions concerning alcohol use (one binary variable and one count variable). The exact questions can be found in Table \ref{tab:table1}. \par

@@

\subsection{Simulations}
\label{sec:2.2}
The first step in the process of creating the simulated datasets was to obtain parameter estimates from \citet{pellowski2016alcohol} and to quantify the relationships between variables. These estimated relationships were treated as the "true" relationships and one thousand samples were drawn using these parameters. The purpose of simulating these datasets was to see how well they captured the true relationship between daily medication adherence on a certain day, whether or not a participant drank that day, and their beliefs about alcohol-medication interactivity (included as a Z-transformed test score). Specifically, our model of interest is the random intercept model with time effect found below: \\

@@

Additionally, for each different Missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 25\%, 50\%, and 75\% missing data. Previous work by \citet{rhemtulla2014planned} found that for low levels of missingness (25\%) the Three-Form design outperforms the Wave Missingness design in capturing latent growth curve model parameters. However, because only low-levels of missingness are tested it is unknown whether this relationship holds at moderate or high levels. We hope that by including these different levels of missingness we will be able to see how these designs perform at all levels of the missingness spectrum. \par
Once missingness was created, Multiple Imputation techniques were applied to estimate the relationship between medication adherence and the other variables in our model. Because we have control over the missing data mechanism, we know the data is MCAR. This fact allows for the principled use of MI techniques. Using the R package $\{$mice$\}$ \citep{mice2011imputation} our binary variables (Q1-Q7) were imputed using a logistic model based approach while the count variable (Q8) was imputed using predictive mean matching. \par

After imputating, a logistic random-intercept model was estimated for each of the imputed datasets and combined using Rubin's Rules \citep{rubin2004multiple}. From here, the results from each PM design were evaluated based on bias, percent bias, mean squared error (MSE), coverage, confidence interval (CI) length, and the fraction of missing information (FMI). The FMI is a measure of how much of the MI sample variance comes from differences between imputations. In addition to comparing the results between each of the PM designs, the same analyses were also performed before missingness was imposed. \par

When determining if the PM designs are performing sufficiently, it is important to consider how well the simulated samples performed before adding a missingness structure. For example, consider two full data samples with respective biases on the $\beta_1$ estimate of 0.13 and 0.15. Further, after imposing different PM design structures on these samples, the average biases are 0.14 and 0.15 respectively. It would be unfair to claim that the first PM design performed better than the second because, by chance, it was based off of a more representative sample. This fact was considered when determining the evaluation criteria. \par

For bias, percent bias, and MSE we claimed that an increase of more than 40\% in these measurements after imposing missingness indicates that the PM design is inappropriate. For instance, if the complete data shows a percent bias of 10\%, anything higher than 14\% would be unacceptable. An increase of this size has the ability to negatively effect efficiency of our estimation. Based on the work of \citet{collins2001comparison} we also regard coverages of less than 90\% as unacceptable. If a 95\% CI has a true coverage of 90\% than the Type I error rate is double what it should be. Because MI accounts for uncertainty in the imputation process, coverages should be similar despite the added missingness. In terms of confidence interval lengths, if one PM design provides similar rates of coverage to another while maintaining shorter intervals than this is considered the better of the two methods. For equal coverage rates, shorter intervals imply more power. The FMI, which quantifies the uncertainty in our imputation process, is simply reported for each PM design. While less uncertainty in the imputations can be beneficial, less variation does not necessarily imply accuracy. Thus, FMI should be taken in the context of the other measurements. \par

This process was repeated under the three modified simulation scenarios mentioned in the following sections. Note that while typically these PM designs would be compared against the results obtained using a complete case analysis \citep{rhemtulla2016asymptotic}, this approach was avoided as it would fundamentally alter the form of the data. Specifically, complete case analysis removes any observation with any missing values. Then, for the Split Form design this would remove all observations. In the Wave Missingness setup, complete case analysis would shorten the length of the longitudinal study. If a participant was missing values on 11 of the 45 days, then complete case analysis would have made the data resemble a longitudinal study held over 34 days. Hence, this comparison is invalid. \par

\subsubsection{Increased Sample Size}
In order to evaluate the impact of sample size on estimation, the original sample size of 60 participants was expanded to 120. The rest of the simulation process was carried out as before. As noted earlier, the cost savings gleaned from the PM designs could allow us to enroll more participants. Thus, even if one design performed more optimally than the others, if all designs also perform acceptably well at high samples, researchers can design missingness in whichever method is most convenient. Furthermore, because Wave Missingness allows for greater savings, an increase in sample size is more reasonable for that type of missingness. \par
\subsubsection{Low Inter-Survey Correlation}
For our second simulation scenario we looked to determine the effect of decreased inter-survey correlation on which PM design would perform best. To clarify, consider the fact that answers given on a particular day may be correlated with one another- the two questions on housing insecurity, for example, are likely to be "yes" on the same days. While this fact was accounted for in the original simulations, it was not in this set of simulations. If the probability of answering "yes" on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations, then in this scenario it is a function of only the baseline variables. This implies that each of the questions are conditionally independent of each other given the baseline variables. If researchers have a questionnaire where they do not expect any of the answers to be obviously related the results here may help to choose which missingness design would be most optimal. \par
\subsubsection{High Time Effect}
In the final scenario, the goal was to determine which PM design would lead to the best estimates when time has a disproportionately large effect on our outcome variable. To do this we changed the value of the parameters $\gamma_0, \beta_1, \beta_2,$ and $\beta_3$ to -4.6, 0.28, 0.64, and 0.2 respectively. Note that instead of increasing the value of $\beta_3$, the slope for time effect, all the other parameters were decreased. This was done because $\beta_3$ was already fairly large and increasing its value further would cause the probability of missing a dose to rapidly approach 1. Decreasing the other variables effects ensured that time has a disproportionate effect without this problem. The results of this section may prove useful to researchers who believe that the overall passage of time plays a larger role in their outcome than a measurement taken at one specific point. \par

\section{Results}
\label{sec:3}
\subsection{Primary Simulation}
\label{sec:3.1}
The first set of simulations run contained the parameters in the random-intercept logistic model with $\gamma_0 = -2.3$, $\beta_1 = 0.56$, $\beta_2 = 1.28$, and $\beta_3 = 0.2$. The effects of the variables here are comparable to those found in the original dataset. This fact implies that we can interpret the results here to show what may have occurred if the original study had implemented a PM design. Before we imposed a missingness structure on the 1,000 simulated samples we obtained the full data results shown in Table \ref{tab:table2}. Note that the full data results for the other simulation scenarios are also provided in this table for ease of reference.

<<>>=
load("~/designedmissingnessGit/Results/tables20180509_60_1_high.RData")
high <- d

load("~/designedmissingnessGit/Results/tables20180509_60_1_med.RData")
med <- d

load("~/designedmissingnessGit/Results/tables20180509_60_1_low.RData")
low <- d

@@

load("~/designedmissingnessGit/Results/tables20180509_60_1_high_hightime1.RData")
high <- d

load("~/designedmissingnessGit/Results/tables20180509_60_1_med_hightime1.RData")
med <- d

load("~/designedmissingnessGit/Results/tables20180509_60_1_low_hightime1.RData")
low <- d

@@

Of note in the complete-data primary analysis is that the coverage of the 95\% CIs is larger than expected for the parameter estimates and the percent bias for the $\beta_1$ estimate is somewhat large. This increased bias is likely due to the difficulties inherent in estimating logistic regression models with rare event data \citep{king2001logistic}. Nevertheless, we should keep this in mind when analyzing our results from the PM designs provided in Table \ref{tab:table3}. In Table \ref{tab:table3} as in Tables \ref{tab:table4}, \ref{tab:table5}, and \ref{tab:table6} bold values indicate "Unacceptable" results. That is, bias, percent bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.

@@

For the Split Form and Altered Split Form designs seen in Table \ref{tab:table3}, note that the greatest loss in efficiency was on the $\beta_1$ estimate. While the CI coverage remained high at all levels of missingness for the two designs, the bias, percent bias, and MSE reached unacceptable levels at the high missingness level. We also point out that the Altered Split Form design did not perform significantly better than the regular Split Form design. While some individual measurements outperformed those from the Split Form design, bias on $\beta_1$ for example, it underperformed in others, such as percent bias on $\beta_3$. In reference to the FMI on the $\beta_1$ estimate, we can see that at low and medium missingness both Split Form designs performed well. That is, there was less variance in the results from th imputed datasets than we expected given the amount of missing data.\par

Towards the bottom of Table \ref{tab:table3}, the Wave Missingness design provided unacceptable results on bias, percent bias, and MSE for the $\beta_1$ estimate at both medium and high levels of missingness. Moreover, at high levels of missingness coverage became unacceptable as coverage probabilities of the 95\% CIs dropped to 88.5\%.  Additionally, we see that CI length for the $\beta_1$ estimate was roughly equal across all designs, despite the fact that the Wave Missingness design provided more biased estimates. \par

\subsection{Increased Sample Size}
\label{sec:3.2}
In the next simulation scenario the sample size was increased to 120 participants. All parameter values were held the same as in the original simulation. Table \ref{tab:table2}, again, contains the results of the analysis before applying any PM design. \par

The results of the full-data simulations are compared to those obtained from the PM designs, shown in Table \ref{tab:table4}. First notice the bias of all parameters is lower than in the smaller sample size simulations. Next, the Split Form design performed similarly well as in the first. At low levels of missingness it gave acceptable results for bias, percent bias, and MSE for the $\beta_1$ and for medium levels only the MSE was unacceptable. However, the CI length is relatively far from the complete-data measurement in Table \ref{tab:table2}. The CI length from the complete-data simulations was 0.460 while at high levels of missingness the CI length reaches 1.088. Furthermore, the percent bias on the $\beta_1$ estimate is not seriously different from that obtained in the small sample scenario. For example, at medium levels of missingness the percent bias on $\beta_1$ is 23.86\% while for the smaller sample it was 23.75\%.
Similarly to the Split Form design, the Altered Split Form Design also provided unacceptable results for the MSE of the $\beta_1$ estimate at medium missingness and unacceptable bias, percent bias, and MSE at high levels.  \par
For the Wave Missingness design we continue to see the issues observed in the small sample simulations. That is, for the $\beta_1$ estimate the measurements at medium and high levels of missingness are unacceptable and a steep drop off in coverage probability occurs for the 95\% CIs. In fact, at medium and high levels of missingness the coverages drop to 85.5\% and 82.0\%. The $\gamma_0$ parameter also continues to be estimated poorly at high levels of missing data under the Wave Missingness design. \par

\subsection{Low Inter-Survey Correlation}
\label{sec:3.3}
For the next set of simulations sample size returned to 60 participants but the level of inter-survey correlation decreased. The results obtained from the full data simulations are provided in Table \ref{tab:table2} while the results from the PM designs are given in Table \ref{tab:table5}. \par

For the Split Form design it is important to notice that the efficiency of the $\beta_1$ estimate decreases much more rapidly than in the original simulations where survey questions were predictive of one another. For instance, the bias of $\beta_1$ at low levels of missingness, here, was found to be 0.150 and 0.276 at high levels. This left us with an increase in average bias of 0.126. Looking at the same increase in the original simulations, note that the bias only increased by 0.071. This loss in efficiency is seen in the other measurements on the $\beta_1$ estimate as well. Moreover, note that the Split Form design performs unacceptably in terms of bias, percent bias, and MSE at medium levels of missingness. This was not the case in the other missingness scenarios. \par

The Altered Split Form design at medium levels of missingness yielded an MSE outside of the acceptable range and at high levels bias, the percent bias are unacceptable as well. Additionally, the coverage of the $\beta_1$ CIs was quite a bit higher than in the full-data simulations. That is, while the coverage probability obtained in the full-data simulations was 94.5\%, under this Altered Split Form design the coverages are 95.5\%, 97.0\%, and 96.0\% at low, medium, and high levels of missingness respectively. \par

Under Wave Missingness the issues of unacceptable bias, percent bias and MSE occur. However, at low levels of missingness, the coverage of the $\beta_1$ estimate was fairly good (96.5\% compared to 94.5\% in the full data). Sufficient coverage did not hold through increased missingness as coverage dropped to 89.5\% in the high missingness scenario. As in other scenarios, the CI lengths produced under the Wave Missingness design are similar to those produced in the Split Form designs despite an increase in bias. However, here the increase in bias is less dramatic than in other scenarios. For example, at high levels of missingness in the original simulations the average bias on the $\beta_1$ estimate was 0.065 higher for the Wave Missingness design (at 0.290) than in the Split Form design (0.225). In this simulation scenario that same difference was only 0.027. Moreover, while the estimation of $\gamma_0$ was unacceptable at high levels of missingness in the other simulation scenarios, here it was in the acceptable range.\par

\subsection{High Time Effect}
\label{sec:3.4}
In the final scenario we tested to see how the PM designs would capture a model where time had a disproportionately large effect on Missed Dose. In this scenario parameter values were changed to $\gamma_0 = -4.6$, $\beta_1 = 0.28$, $\beta_2 = 0.64$, and $\beta_3 = 0.2$. The results from our full-data analyses are provided in Table \ref{tab:table2} while the corresponding PM design results are in Table \ref{tab:table6}. \par

@@

The Altered Split Form design performed slightly better than the normal Split Form design under this simulation scenario. Note, however, that while the normal Split Form design provided unacceptable bias and percent bias for the $\beta_1$ estimate at medium levels of missingness, this was not true of the Altered Split Form design. Additionally, observe that at medium and high levels of missingness there was an improvement under the Split Form design in the CI lengths for the $\beta_1$ estimate. In the Split Form design the CI lengths were recorded as 0.981 and 1.433 at medium and high missingness. Under the Altered Split Form design these measurements were 0.903 and 1.381. \par
